### 2016-08-23 section/0_intro.tex
check in Linhai's updates

Performance bug detection tools use static or dynamic analysis to identify
code regions that match specific inefficiency patterns 
\cite{Alabama,CARAMEL, Cachetor,Xu:2010:FLD:1806596.1806617,Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616,IsilDillig.PLDI15}. 
Unfortunately, these tools are not designed for and are consequently
unsuitable for performance diagnosis.
They are not designed to provide \textit{coverage} for a wide
variety of real-world problems; their analysis is not guided by
performance failure symptom, and hence are at disadvantage in terms of diagnosis
\textit{accuracy}; dynamic detection tools often lead to 
10X slowdowns or more \cite{Cachetor,Xu:2010:FLD:1806596.1806617,Alabama}, 
not ideal in terms of \textit{performance}.

@@

\subsection{Contributions}
This paper presents a tool, \Tool, that can help effectively diagnose
inefficient loop problems, the most common type of performance problems
\cite{SongOOPSLA2014,PerfBug}, with good coverage, accuracy, and performance.

>>>>

Performance bug detection tools use static or dynamic analysis to identify
code regions that match specific inefficiency patterns 
\cite{Alabama,CARAMEL, Cachetor,Xu:2010:FLD:1806596.1806617,Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616,IsilDillig.PLDI15}. 
Unfortunately, these tools are not designed %for
{\color{red} to identify code regions for a specific execution slowness}  
and are consequently
unsuitable for performance diagnosis.
They are not designed to provide \textit{coverage} for a wide
variety of real-world problems; their analysis is not guided by
performance failure symptom, and hence are at disadvantage in terms of diagnosis
\textit{accuracy}; dynamic detection tools often lead to 
10X slowdowns or more \cite{Cachetor,Xu:2010:FLD:1806596.1806617,Alabama}, 
not ideal in terms of \textit{performance}.

@@

\subsection{Contributions}
This paper presents a tool, \Tool, that can help effectively diagnose
inefficient loop problems, the most common type of performance problems
\cite{SongOOPSLA2014,PerfBug}, with good coverage, accuracy, and performance.
{\color{red} \Tool does not target identifying previously unknown performance bugs, 
but aims to provide root causes for execution slowness caused by inefficient loops.}

### 2016-08-23 section/3_redundancy.tex
check in Linhai's updates

\subsection{Fix Strategy Recommendation}
\label{sec:redundant_fix}
\Tool suggests how to fix an inefficient loop to developers.
This process is straightforward following our taxonomy discussion in 
Section \ref{sec:study}, as there is often only one or two natural fix 
strategies for each sub-category of root causes.

Once a loop is identified as \emph{resultless}, \Tool will suggest
the loop to be completely deleted, in case of 0$^*$ resultless, or
conditionally skipped, in case of [0$|$1]*; \Tool will suggest a 
data-structure change in case of 0*1? loops.

@@

For cross-iteration redundancy, \Tool suggests batching if the
redundancy is related to I/O operations and suggests memoization otherwise.
Specifically, 
when the only side effect of a loop is from I/O operations
and the same statement(s) is executed in every loop iteration, \Tool reports 
this
as an I/O related redundancy problem and suggests batching as a potential fix
strategy. Otherwise, \Tool suggests memoization.

For cross-loop redundancy, whether to use memoization or batching often
depends on which strategy is cheaper.
\Tool uses a simple
heuristic. If 
the side effect of each loop instance is to update 
a constant number of memory locations, like the 
buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
we recommend memoization. Instead, if the side effect is to update
a sequence of memory locations, with the number of locations increasing
with the workload, memoization is unlikely to save much and
hence batching is suggested.

In addition to the above high-level fix strategies, \Tool can also provide some 
detailed information to help developers design the patch.
For example, in case of memoization fix strategy,
since \Tool knows what exactly are the memory reads that return the same values
again and again, it can help decide what to memoize; in case of
I/O-related batching, \Tool points out the exact I/O operations that should
be considered batching; and so on. 
Generating complete patches is out of the scope of \Tool.

>>>>

\subsection{Fix Strategy Recommendation}
\label{sec:redundant_fix}

\Tool suggests how to fix an inefficient loop 
{\color{red} and provides related information for carrying out that fix} 
to developers.
This process is straightforward following our taxonomy discussion in 
Section \ref{sec:study}, as there is often only one or two natural fix 
strategies for each sub-category of root causes.

Once a loop is identified as \emph{resultless}, \Tool will suggest
the loop to be completely deleted, in case of 0$^*$ resultless, or
conditionally skipped, in case of [0$|$1]*; \Tool will suggest a 
data-structure change in case of 0*1? loops.
{\color{red}Besides these fix strategies, \Tool also reports side-effect instructions 
and what percentage of loop iterations executing each such instruction. 
These information can help developers refactor the loop or change data structures processed by the loop. }

@@

For cross-iteration redundancy, \Tool suggests batching if the
redundancy is related to I/O operations and suggests memoization otherwise.
Specifically, 
when the only side effect of a loop is from I/O operations
and the same statement(s) is executed in every loop iteration, \Tool reports 
this
as an I/O related redundancy problem, 
{\color{red}pointing out I/O instructions,} 
and suggests batching as a potential fix
strategy. Otherwise, \Tool suggests memoization, 
{\color{red}and provides information for input instructions and redundancy rate.}

For cross-loop redundancy, whether to use memoization or batching often
depends on which strategy is cheaper.
\Tool uses a simple
heuristic. If 
the side effect of each loop instance is to update 
a constant number of memory locations, like the 
buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
we recommend memoization. Instead, if the side effect is to update
a sequence of memory locations, with the number of locations increasing
with the workload, memoization is unlikely to save much and
hence batching is suggested.
{\color{red} \Tool will also provide information for input instructions and side-effect instructions to developers. }

{\color{red} [redundant]
In addition to the above high-level fix strategies, \Tool can also provide some 
detailed information to help developers design the patch.
For example, in case of memoization fix strategy,
since \Tool knows what exactly are the memory reads that return the same values
again and again, it can help decide what to memoize; in case of
I/O-related batching, \Tool points out the exact I/O operations that should
be considered batching; and so on. 
Generating complete patches is out of the scope of \Tool.
}

### 2016-08-23 section/5_exper.tex
check in Linhai's updates

\begin{table}
  \centering
  %\scriptsize
  \tiny
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  $<0.01\%\pm0.73\%$  & $18.29\%\pm1.33\%$       &  $18.84\%\pm4.44\%$  & 355.51{\bf X}$\pm$8.59{\bf X} & 661.49{\bf X}$\pm$81.63{\bf X} \\ 
    Mozilla416628 &  $<0.01\%\pm1.76\%$  & $4.87\%\pm2.09\%$        &  $2.41\%\pm1.58\%$   & 72.52{\bf X}$\pm$1.57{\bf X}  & 112.15{\bf X}$\pm$2.01{\bf X} \\
    \midrule
     MySQL27287   &  $5.47\%\pm1.29\%$   & $0.20\%\pm2.04\%$        &   -                  & 263.74{\bf X}$\pm$8.50{\bf X} & 880.95{\bf X}$\pm$101.24{\bf X} \\
     MySQL15811   &  -                   & $0.35\%\pm2.81\%$        &   -                  & 413.59{\bf X}$\pm$53.94{\bf X}& 1087.16{\bf X}$\pm$43.26{\bf X} \\
    \midrule
      GCC46401    &  $<0.01\%\pm0.17\%$  & $<0.01\%\pm0.27\%$       &  $<0.01\pm0.22\%$    & 32.89 {\bf X}$\pm$0.38{\bf X} & 59.07{\bf X}$\pm$1.24{\bf X}\\ 
      GCC1687     & -              & /                 &  $1.84\%\pm0.28\%$                &   /                           & 223.30{\bf X}$\pm$17.75{\bf X} \\
      GCC27733    & $<0.01\%\pm0.26\%$   & /           &  $<0.01\%\pm0.25\%$               &   /                           & 18.44{\bf X}$\pm$0.32{\bf X}     \\
      GCC8805     & -              & $0.50\%\pm1.26\%$ &  $0.19\%\pm1.43\%$                & 2.89{\bf X}$\pm$0.35{\bf X}    & 3.36{\bf X}$\pm$0.44{\bf X}\\
      GCC21430    & -              & $4.86\%\pm0.81\%$ &  $2.37\%\pm1.38\%$                & 164.02{\bf X}$\pm$20.35{\bf X} & 254.9{\bf X}$\pm$22.34{\bf X} \\
      GCC12322    & -              & $4.77\%\pm2.48\%$ &  $<0.01\%\pm2.24\%$               & 25.56{\bf X}$\pm$2.50{\bf X}  & 24.87{\bf X}$\pm$2.52{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop
    (only non-extracted benchmarks are shown). 
  -: dynamic analysis is not needed;
  /: not applicable.}
  \label{tab:performance}
\end{table}

>>>>

\begin{table*}[tb!]
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccccc}
    \toprule
	    & \multicolumn{2}{c}{execution time} & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-3}
     \cmidrule(lr){4-6}
     \cmidrule(lr){7-8}
     {\bf BugID}  & {\bf Buggy}  & {\bf Patched} & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  $1.52\pm1.80*10^{-2}$ & $5.37*10^{-2}\pm3.77*10^{-3}$  &  $<0.01\%\pm0.73\%$  & $18.29\%\pm1.33\%$       &  $18.84\%\pm4.44\%$  & 355.51{\bf X}$\pm$8.59{\bf X} & 661.49{\bf X}$\pm$81.63{\bf X} \\ 
    Mozilla416628 &  $4.29*10^{-1}\pm6.70*10^{-3}$  & $1.15*10^{-1}\pm4.64*10^{-3}$  &  $<0.01\%\pm1.76\%$  & $4.87\%\pm2.09\%$ &  $2.41\%\pm1.58\%$ & 72.52{\bf X}$\pm$1.57{\bf X}  & 112.15{\bf X}$\pm$2.01{\bf X} \\
    \midrule
     MySQL27287   & $1.21\pm1.77*10^{-2}$& $2.03*10^{-2}\pm3.45*10^{-4}$ &  $5.47\%\pm1.29\%$   & $0.20\%\pm2.04\%$  &   - & 263.74{\bf X}$\pm$8.50{\bf X} & 880.95{\bf X}$\pm$101.24{\bf X} \\
     MySQL15811   & $1.65\pm1.67*10^{-2}$& $8.39*10^{-2}\pm6.64*10^{-3}$          &  -                   & $0.35\%\pm2.81\%$        &   -                  & 413.59{\bf X}$\pm$53.94{\bf X}& 1087.16{\bf X}$\pm$43.26{\bf X} \\
    \midrule
      GCC46401    & $3.21\pm7.92*10^{-3}$ & $6.56*10^{-2}\pm3.68*10^{-3}$          &  $<0.01\%\pm0.17\%$  & $<0.01\%\pm0.27\%$       &  $<0.01\pm0.22\%$    & 32.89 {\bf X}$\pm$0.38{\bf X} & 59.07{\bf X}$\pm$1.24{\bf X}\\ 
      GCC1687     & $2.99\pm7.78*10^{-3}$ & $0.68*10^{-2}\pm8.12*10^{-4}$          & -              & /                 &  $1.84\%\pm0.28\%$                &   /                           & 223.30{\bf X}$\pm$17.75{\bf X} \\
      GCC27733    &  $10.50\pm1.20*10^{-2}$ & $0.80\pm1.99*10^{-2}$           & $<0.01\%\pm0.26\%$   & /           &  $<0.01\%\pm0.25\%$               &   /                           & 18.44{\bf X}$\pm$0.32{\bf X}     \\
      GCC8805     & $2.40\pm2.36*10^{-2}$  & $0.28\pm1.73*10^{-2}$          & -              & $0.50\%\pm1.26\%$ &  $0.19\%\pm1.43\%$                & 2.89{\bf X}$\pm$0.35{\bf X}    & 3.36{\bf X}$\pm$0.44{\bf X}\\
      GCC21430    & $3.27\pm2.02*10^{-2}$             & $0.66\pm1.06*10^{-2}$          & -              & $4.86\%\pm0.81\%$ &  $2.37\%\pm1.38\%$                & 164.02{\bf X}$\pm$20.35{\bf X} & 254.9{\bf X}$\pm$22.34{\bf X} \\
      GCC12322    & $47.68\pm1.01$       & $3.06\pm8.67*10^{-3}$          & -              & $4.77\%\pm2.48\%$ &  $<0.01\%\pm2.24\%$               & 25.56{\bf X}$\pm$2.50{\bf X}  & 24.87{\bf X}$\pm$2.52{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop
    (only non-extracted benchmarks are shown). 
  -: dynamic analysis is not needed;
  /: not applicable;
  execution time is measured in seconds;
  $95\%$ confidence interval is calculated by running each benchmark 10 times.}
  \label{tab:performance}
\end{table*}
